### 2022-11-05 dissertation/chapters/06-bayesian-hyper-heuristic.tex
🚧 (chapter6): Review in progress

\chapter{Bayesian Hyper-Heuristic}
\label{chap:bhh}

\begin{quote}
      \textit{
            ``The result is a posterior distribution which the agent may use as its new prior in the next step.'' - Pedro Domingos, The Master Algorithm: How the Quest for the Ultimate Learning Machine Will Remake Our World.
      }
\end{quote}

The above quote was the inspiration for the development of a novel \ac{HH} that uses \index{Bayesian}\textit{Bayesian} probability concepts as a selection mechanism to drive the heuristic selection process. Thus far the reader was presented with all of the necessary background information on \acp{ANN} in Chapter \ref{chap:anns}, low-level \index{heuristic}heuristics/\index{Optimiser}optimisers in Chapter \ref{chap:heuristics}, \acp{HH} in Chapter \ref{chap:hhs}  and lastly, \index{probability theory}probability theory in Chapter \ref{chap:probability}. These elements form the fundamental components that make up the proposed \Ac{BHH}. A detailed specification on the \Ac{BHH} can now be formulated. This chapter provides the detail around the theory, concept and implementation of the \Ac{BHH} and explains how it used to train \acp{ANN}. It is shown throughout this chapter that the \Ac{BHH} implements a probabilistic optimisation technique that implements and biases a \index{Gaussian Process}\textit{Gaussian process} towards good optimisation and performance. The remainder of the chapter is structured as follows:

\begin{itemize}
      \item \textbf{Section \ref{sec:bhh:overview}} provides a brief overview of the \Ac{BHH} optimiser.

      \item \textbf{Section \ref{sec:bhh:architecture}} presents the general architecture, \Ac{HH} framework and the various components that make up the \index{Optimiser}optimiser.

      \item \textbf{Section \ref{sec:bhh:heuristic_pool}} discusses the collection of low-level \index{heuristic}heuristics, referred to as the \index{heuristic}\textit{heuristic pool} and puts emphasis on the importance of a diverse set of low-level \index{heuristic}heuristics.

      \item \textbf{Section \ref{sec:bhh:entity_pool}} discusses the detail of the \index{Population}population and its \index{entity}entities, with specific detail provided on entity (local) and population (global) state and memory.

      \item \textbf{Section \ref{sec:bhh:initialisation_step}} presents the initialisation strategy in detail.

      \item \textbf{Section \ref{sec:bhh:selection_mechanism}} presents the \index{Bayesian}\textit{Bayesian} probabilistic model that is used as a selection mechanism.

      \item \textbf{Section \ref{sec:bhh:heuristic_entity_selections}} discusses heuristic-entity selections and how these two concepts are utilised together.

      \item \textbf{Section\ref{sec:bhh:model}} discusses the models that can be optimised using the \Ac{BHH}, specifically referring to its application to training \acp{FFNN}.

      \item \textbf{Section \ref{sec:bhh:train_test_datasets}} briefly discussed the role of the train and test datasets during training.

      \item \textbf{Section \ref{sec:bhh:loss_function}} discusses model evaluation and the role of the loss/cost function.

      \item \textbf{Section \ref{sec:bhh:domain_barrier}} discusses the domain barrier that exists between the high-level \ac{BHH} and low-level heuristics in the \index{heuristic pool}heuristic pool.

      \item \textbf{Section \ref{sec:bhh:performance_log}} presents the performance log and discusses performance measurement in more detail.

      \item \textbf{Section \ref{sec:bhh:credit_assignment_strategy}} discussed credit assignment and move acceptance strategies in detail.

@@

      \item The pseudo-code algorithm for the \ac{BHH} is given in \textbf{Section \ref{sec:bhh:algorithm}}.

      \item Finally, a summary of the chapter is provide in \textbf{Section \ref{sec:bhh:summary}}.
\end{itemize}

\section{Overview}
\label{sec:bhh:overview}

This section provides an overview of the workings of the \Ac{BHH}. To start the discussion, consider the following analogy:\\
\\
\textit{
      Bob is a teacher at a high school. Every year his students perform really well and he wins the prize for best teacher, evaluated by student performance. He is able to do this not just because he is a good teacher, but he understands that each student has a learning technique that works best for him/her. He exploits this concept by tailoring the teaching process to each students such that the result is an optimum mark for that student and by definition, the whole class. Bob knows that it is too timely to get to know each student, so he devises a model that does the allocations for him. This model uses a process of observation. With each evaluation opportunity he experiments by allocating different learning techniques to different students. He evaluates the student for the given opportunity and keeps a log of which learning technique he assigned to the student as well as the outcome. With each evaluation opportunity he updates his model by biasing the assignment process such that students generally get assigned learning techniques that yield the best performance for them.
}\\
\\
The key take-out from the analogy above is the concept that Bob can maximise student performance by updating his beliefs, over time, about which learning technique to assign to which (type of) student. He does this by biasing selection/assignment towards the best combinations of student, learning technique
and evaluation opportunity. This is the basic nature of the \Ac{BHH}. The students are analogous to a population of entities. The learning techniques are analogous to heuristics/optimisers. Evaluation opportunities are analogous to optimisation problems to be optimised. Student performance is analogous to optimisation capability and performance measurement. The general goal of the \ac{BHH} can be summarised as aiming to select and managing the appropriate  heuristic/optimiser and update step for each entity, at each optimisation step, while optimising some underlying model, which for this dissertation, is to train \acp{FFNN}.

Formal classification of the \Ac{BHH} is needed. Burke et al.~\cite{ref:burke:2010} proposed a classification mechanism that was discussed in detail in Chapter \ref{chap:hhs}. The same classification mechanism is used to classify the \ac{BHH}. For the first dimension of the classification, the authors propose that the \Ac{BHH} be classified as a \textit{selection} \ac{HH}. For the second dimension of the classification proposed, the authors propose that the \Ac{BHH} be classified as utilising \textit{perturbation} low-level heuristics. Furthermore, the \ac{BHH} is also classified as a population-based approach that includes meta-heuristics. Burke et al.~\cite{ref:burke:2010} further proposed the classification of \acp{HH} according to the source of the feedback used during learning. It can thus be said that the \ac{BHH} employs online learning according to this criteria, classifying it as an \textit{adaptive} \ac{HH}. A \textit{population-based, selection, meta-hyper-heuristic that utilised perturbation of low-level heuristics and online learning} seems like an mouthful, but technically, that is it's full and formal classification. A breakdown and motivation of these classifications is given below:

\begin{itemize}
      \item \textbf{Population-Based:} The \ac{BHH} follows a population-based approach where a number of different \index{candidate solution}candidate solutions, referred to as \index{entity}\textit{entities} work together to yield a global best solution. There is also the concept of a shared global state or memory.

      \item \textbf{Selection:} The \ac{BHH} implements a \index{heuristic}heuristic selection mechanism that selects from a collection of lower level \index{heuristic}heuristics' in a so-called \index{heuristic hool}\textit{heuristic pool}. There is also a measure of acceptance criteria through credit assignment strategies.

      \item \textbf{Meta:} Incorporates the classical/analytical gradient-based low level \index{heuristic}heuristics (typically from the \ac{ML} research space) as well as meta-heuristics such as other population-based \index{Meta-Heuristic}meta-heuristics (typically \ac{EC} research space).

      \item \textbf{Hyper-Heuristic:} There exists a domain barrier where the \ac{BHH} searches through the \textit{heuristic space} while lower level heuristics search through the \textit{solution space}.

      \item \textbf{Perturbation of Low-Level Heuristics:} Refers to the iterative optimisation approach followed by the \ac{BHH}. The \ac{BHH} considers a number of randomly initialised candidate solutions in the form of entities in a population. It is applied in an iterative manner, during the training process. It generally employs the two main processes of \acp{HH} with perturbation of heuristics. These include a \textit{selection step} that selects from low-level heuristics and applies them to entities/candidate solutions. It also includes an \textit{acceptance strategy}. The \ac{BHH} maintains entity and population state through update step operations that proxy update steps from different heuristics. More details on this concept is given later in Section \ref{sec:bhh:heuristic:proxies}.

      \item \textbf{Online Learning:} Refers to the source of the feedback used during training. The \ac{BHH} optimises, at a higher level, the selection and application of the \index{heuristic space}\textit{heuristic space} while low-level heuristics optimise entities' solution to the underlying model, in this case a \ac{FFNN}. This happens during training time, yielding the classification of utilising \textit{online} learning.
\end{itemize}

More detailed consideration of these elements are required. The following sections break down the \Ac{BHH} into its various parts, starting with a discussion on the high-level architecture next.

\index{Architecture}
\section{Architecture}
\label{sec:bhh:architecture}

This section aims to present the reader with all the high level components in the architecture of the \Ac{BHH}. Burke et al.~\cite{ref:burke:2010} proposed an initial framework for \acp{HH} and Grobler~\cite{ref:grobler:2015} further proposed a framework for a heterogeneous meta-\ac{HH}. These frameworks have been adapted for the implementation of the \Ac{BHH}. An illustration of the high-level architecture of the \Ac{BHH} is given in Figure \ref{fig:bhh_architecture} below.

\begin{figure}[H]
      \centering
      \includegraphics[width=1.0\textwidth]{bhh_architecture.png}
      \caption[The \index{Bayesian Hyper-Heuristics}Bayesian Hyper-Heuristic Architecture]{An illustration of
            the architecture and high level components of the \index{Bayesian Hyper-Heuristics}Bayesian Hyper-Heuristic.}
      \label{fig:bhh_architecture}
\end{figure}

At a high level, the architecture presented in Figure \ref{fig:bhh_architecture} above, presents the following main components:

\begin{itemize}
      \item \textbf{Heuristic Pool}: Contains a collection of low-level \index{heuristic}heuristics/\index{optimiser}optimisers. This is the \index{heuristic space}\textit{heuristic} space. Each heuristic has a proxy that is used to relay heuristic state update operations.

      \item \textbf{Entity Pool}: A collection of \index{entity}entities in a \index{population}population. These entities represent candidate solutions to the model. Each entity has its own state, but there is also a shared global population state.

      \item \textbf{Initialisation Step}: This is the execution of some initialisation strategy that determines how the entities in the entity pool (population) and the heuristics in the heuristic pool are initialised.

      \item \textbf{Selection Mechanism}: This is the implementation of the selection mechanism of selection \acp{HH}. In the case of the \ac{BHH}, the selection mechanism is a Bayesian probabilistic model.

      \item \textbf{Heuristic-Entity Selections}: This is the results of the selection mechanism. Heuristics are sampled/selected for each entity. Each entity's state will thus be manipulated by that particular heuristic's proxy methods.

      \item \textbf{Model}: The \index{model}model to be optimised. This forms the problem domain. In the case of this dissertation, the model is a \ac{FFNN}.Technically the model here simply refers to the architectural structure of the model, while entities represent that candidate solution (weights) to the model.

@@

      \item \textbf{Loss/Cost Function}: The loss/cost function is the metric  by which the model is evaluated. In the case of supervised learning, the loss/cost function is a measure of distance between predicted output and the ground truth.

      \item \textbf{Domain Barrier}: A constraint on information flow, prohibiting high level components in the \index{heuristic space}\textit{heuristic} space from interacting and relaying information related to the \index{solution space}\textit{solution} space.

@@

      \item \textbf{Credit Assignment Strategy}: Implements a specific strategy to determine if the performance of an entity-heuristic combination is better than others or not.

      \item \textbf{Update Step}: The high level heuristic update step. This involves the mechanism by with the \ac{BHH} is optimised.
\end{itemize}

The above components are not described in enough detailed to properly illustrate their role in the \Ac{BHH}. To ensure proper clarity is given to each of these elements, a detailed discussion on each of these elements are presented next.

\index{Heuristic Pool}
\section{Heuristic Pool}
\label{sec:bhh:heuristic_pool}

This section discusses the concept of the heuristic pool, as implemented by the \ac{BHH}. Generally speaking, they heuristic pool is just a collection of low-level heuristics and make up the set of possible heuristics to select from. This is referred to as \text{heuristic space}. Importantly, since \acp{HH} optimise in heuristic space, it is from these lower-level heuristics that the \ac{BHH} must select and apply. The heuristic pool can then be defined in terms of size and/or heuristics that are included in the pool. These two aspects pose very important design choices. Both of these concepts can be empirically tested, however, one could argue the choice of design. Fundamentally, these design choices are about diversity. A brief discussion is given next on the trade-offs between exploration, exploitation and capability.

\index{Exploration}
\index{Exploitation}
\subsection{Diversity: Exploration, Exploitation and Capability}
\label{sec:bhh:heuristic_pool:diversity}

As with all \acp{HH}, the heuristics to be included in the heuristic pool is of great importance and should be carefully decided upon. A heuristic's eligibility for inclusion is determined by the following factors:

\begin{itemize}
      \item \textbf{Capability}: Certain heuristics are only capable of solving or optimising for certain problem types and domains. Examples include continuous vs. discrete, differentiable vs.  non-differentiable or static vs. dynamic problems.

      \item \textbf{Exploration and Exploitation Trade-off}: Some heuristics explore or exploit more than others. This could be due to the nature of the implementation or due to some hyper-parameter such as a learning rate.
\end{itemize}

An argument for diversity must thus be made. One of the benefits of \acp{HH} in general is that it will learn which heuristics to apply and when. The trade-off between exploration and exploitation should thus be outsourced to the \ac{BHH} itself. By including a diverse set of heuristics, based on the criteria mentioned above, the \ac{BHH} will learn to select and apply the appropriate heuristic at the appropriate time throughout the training process, naturally balancing a trade-off between exploration and exploitation. Heuristics that initially explore a lot should be selected when exploration is needed and heuristics that exploit a lot should be selected accordingly.

Notice however that diversity can not be achieved by simply including many different heuristics. The \ac{BHH} is still constraint by heuristic pool size. Consider that for every heuristic that is included, the demand for samples size required to learn with statistical certainty exponentially increases. Not only does a large heuristic pool drastically complicate the learning that is required by the \ac{BHH}, but it also drastically complicates the process of maintaining state. The next section provides the concept of heuristic update step proxies, an important component of the \ac{BHH}.

\index{Proxies}
\subsection{Proxies}
\label{sec:bhh:heuristic:proxies}

The concept of proxies arise from the sparsity of state as maintained by different heuristics. Since heuristics maintain different states, there is an uncertainty of state transition when switching between heuristics. Consider an example where the heuristic pool consists of just two heuristics. One heuristic is a gradient-based heuristic that maintains momentum such as \ac{Adam}. The other is a meta-heuristic that does not require a gradient at all such as \ac{PSO}. Both these heuristics track different parameters in their state. For \ac{Adam}, the expected gradient mean and variance is maintained, while the \ac{PSO} maintains record of the gbest and pbest solutions all of entities. A solution to this is to proxy heuristic state update operations. This allows us to maintain state in two parts:

\begin{itemize}
      \item \textbf{Primary State}: This refers to state the is originally maintained by a heuristic. The selected heuristic simply applies the normal state update operations to its state.

      \item \textbf{Proxied State}: This refers to state that is not directly maintained by the current selected heuristic, but can be updated by outsourcing the required state update operation to another heuristic.
\end{itemize}

Effectively this means that both primary and proxied state elements must be maintained together. Since entities represent candidate solutions, which are a form of state, entities are ideal components to store these state parameters. Thus, entities are extended to include the primary state elements of all the underlying low-level heuristics as well as the candidate solution (weights) for the model. At each heuristic-entity application step, all state elements per entity are updated either by primary method or by proxied method. The \ac{BHH} thus incorporates a state update operation proxy mapping as given in the example in Table \ref{tab:bhh:heuristic_pool:proxy_mapping_example} below.

\begin{table}[htbp]
      \centering
      \caption{State update operation proxy mapping example.}
      \label{tab:bhh:heuristic_pool:proxy_mapping_example}%
      \par\bigskip
      \resizebox{0.5\textwidth}{!}{
            \begin{tabular}{ccccc}
                                                                  &   & \multicolumn{3}{c}{State Parameter}                                                                                                                                                                                      \\
                  \cmidrule{3-5}                                  &   & 1                                                                      & 2                                                                      & 3                                                                      \\
                  \cmidrule{3-5}    \multirow{3}[1]{*}{Heuristic} & A & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{n/a} & \cellcolor[rgb]{ 1,  .922,  .612}\textcolor[rgb]{ .612,  .341,  0}{B}  & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{n/a} \\
                                                                  & B & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{n/a} & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{n/a} & \cellcolor[rgb]{ 1,  .922,  .612}\textcolor[rgb]{ .612,  .341,  0}{A}  \\
                                                                  & C & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{n/a} & \cellcolor[rgb]{ 1,  .922,  .612}\textcolor[rgb]{ .612,  .341,  0}{B}  & \cellcolor[rgb]{ 1,  .922,  .612}\textcolor[rgb]{ .612,  .341,  0}{A}  \\
            \end{tabular}%
      }
\end{table}%

From the example given in Table \ref{tab:bhh:heuristic_pool:proxy_mapping_example}, when heuristic A is selected, it will outsource state update operations from heuristic B, for state parameter 2. Heuristic B will outsource from heuristic A, for state parameter 3. Finally, heuristic C will outsource from heuristic A and B, for state parameters 2 and 3 respectively. In this way, all heuristics maintain all the state parameters.

Notice however that this is a simple concept in principle, but requires detailed decomposition of the heuristics included in the heuristic pool.  Overlapping and unique state parameters must be identified so that a proxy mapping such as the one given in Table \ref{tab:bhh:heuristic_pool:proxy_mapping_example} can be constructed. A suggestion to simplify this process is to borrow concepts from the equations of motion from physics. These include \textit{position}, \textit{velocity}, \textit{acceleration} and \textit{momentum}. Expressing heuristic update steps according to these parameters drastically simplify the process. However, it is possible that heuristics implement unique state parameters that do not overlap, these have to be catered for in the proxy mapping.

These state parameters and update operations should not be considered in isolation. An example of this is position and velocity. Consider for example heuristics such as \acl{DE} and \aclp{GA}. These heuristics recombine entities. In this case, the concept of an equation of motion does not entirely make sense, since the displacement of its position is not a result of maintaining velocity or momentum, but rather by pure displacement through recombination. In this particular case, a solution to this is to apply the recombination operation to all secondary state parameters as well or to nullify secondary state parameters. Unfortunately there is no general solution and each heuristic must be carefully considered. The \ac{BHH} incorporates both of these approaches. The next section provides the reader with details around the entity pool.

\index{Entity Pool}
\section{Entity Pool}
\label{sec:bhh:entity_pool}

This section presents the details around the \index{entity pool}\textit{entity pool}. The \index{entity pool}entity pool refers to a collection of so-called individual \index{entity}\textit{entities}. A common naming convention for such a collection is a \textit{population} of entities. Similar to the heuristic pool that was described in Section \ref{sec:bhh:heuristic_pool} above, the entity pool size is an important design choice. The correct population size is thus a hyper-parameter that can be empirically evaluated.

The entity pool maintains two different types of state. These include entity (local) and population (global) state. Each of these are discussed in more detail next.

\index{Entity State}
\subsection{Entity State}
\label{sec:bhh:entity_pool:entity_state}

>>>>

\chapter{Bayesian Hyper-Heuristic}\label{chap:bhh}

\begin{quotation}
      \noindent ``The result is a posterior distribution, which the agent may use as its new prior in the next step.''
\end{quotation}
\begin{flushright}
      - Pedro Domingos, The Master Algorithm
\end{flushright}

\noindent
The above quote was the inspiration for the development of a novel \acf{HH} that uses Bayesian probability concepts as a selection mechanism to drive the heuristic selection process. Thus far the reader has been presented with all of the necessary background information on \acp{ANN} (Chapter \ref{chap:anns}), low-level \index{heuristic}heuristics (Chapter \ref{chap:heuristics}), \acp{HH} (Chapter \ref{chap:hhs}) and lastly, probability theory(Chapter \ref{chap:probability}). These elements form the fundamental components of the proposed \Acf{BHH}. This chapter provides the details around the implementation of the \Ac{BHH} and explains how it used to train \acp{FFNN}. The remainder of the chapter is structured as follows.

\begin{itemize}
      \item \textbf{Section \ref{sec:bhh:overview}} provides a brief overview of the \Acs{BHH}.

      \item \textbf{Section \ref{sec:bhh:architecture}} provides the general architecture and \Ac{HH} framework implemented by the \Acs{BHH}.

      \item \textbf{Section \ref{sec:bhh:heuristic_pool}} presents the \index{heuristic}\textit{heuristic pool}, a collection of low-level \index{heuristic}heuristics. Discussions follow on the importance of diversity amoungst heuristics in the \index{heuristic pool}heuristic pool.

      \item \textbf{Section \ref{sec:bhh:entity_pool}} presents details on entity (local) and population (global) memory (state).

      \item \textbf{Section \ref{sec:bhh:heuristic_entity_selections}} presents discussions on heuristic-entity selections.

      \item \textbf{Section \ref{sec:bhh:model}} presents the models that can be optimised using the \Acs{BHH}, specifically referring to the training of \acp{FFNN}.

      \item \textbf{Section \ref{sec:bhh:train_test_datasets}} presents a brief discussion on the role of datasets for training and testing.

      \item \textbf{Section \ref{sec:bhh:loss_function}} presents discussions on model evaluation and the role of the loss function.

      \item \textbf{Section \ref{sec:bhh:domain_barrier}} presents discussions on the domain barrier, an information barrier that exists between the high-level \acs{BHH} and low-level heuristics in the \index{heuristic pool}heuristic pool.

      \item \textbf{Section \ref{sec:bhh:performance_log}} presents detailed discussions on performance measurement. The \textit{performance log}, implemented by the \acs{BHH}, is presented.

      \item \textbf{Section \ref{sec:bhh:credit_assignment_strategy}} presents detailed discussions on credit assignment and move acceptance strategies.

      \item \textbf{Section \ref{sec:bhh:selection_mechanism}} presents the Bayesian probabilistic model that is used as the heuristic selection mechanism.

      \item \textbf{Section \ref{sec:bhh:initialisation_step}} presents the initialisation strategy.

@@

      \item \textbf{Section \ref{sec:bhh:algorithm}} provides the pseudo-code algorithm for the \ac{BHH}.

      \item \textbf{Section \ref{sec:bhh:summary}} provides a brief summary of the chapter.
\end{itemize}

\section{Overview}\label{sec:bhh:overview}

This section provides an overview of the workings of the \Acf{BHH}. The general concept of the \acs{BHH} can be summarised as follows. The \acs{BHH} implements a high-level heuristic selection mechanism that learns to select the best heuristic, from a pool of low-level heuristics, to apply to a population of entities, each implementing a candidate solution to a \acs{FFNN}, with the intent of both optimising the underlying \acs{FFNN} and \acs{FFNN} training process. The \acs{BHH} does so by learning the probability that a given heuristic will perform well at a given stage in the \acs{FFNN} training process. These probabilities are then used as heuristic selection probabilities in the next step of the training process.

Formal classification of the \Acs{BHH} is needed. Chapter \ref{chap:hhs} presented the reader with a proposed classification scheme for \acp{HH} by~\citeauthor{ref:burke:2010}~\cite{ref:burke:2010}. According to the aforementioned classification scheme, the \Acs{BHH} is a population-based, meta-hyper-heuristic that utilises selection and perturbation of low-level heuristics in an online learning fashion. A breakdown of the classification is given as follows.

\begin{itemize}
      \item \textbf{Population-Based:} The \ac{BHH} implements a population-based approach, where a collection of different candidate solutions, referred to as \textit{entities}, work together to yield a global best solution.

      \item \textbf{Meta-Hyper-Heuristic:} There exists a domain barrier, where the \ac{BHH} searches through the \textit{heuristic space}, using only \index{heuristic}heuristic performance information, while lower level heuristics search through the \textit{solution space} using information from the search domain itself. Furthermore, the \index{heuristic pool}heuristic pool implemented by the \acs{BHH} supports both gradient-based low level \index{heuristic}heuristics, as well as meta-heuristics.

      \item \textbf{Selection and Perturbation of Low-Level Heuristics:} The \acs{BHH} implements a \index{heuristic}heuristic selection mechanism that selects from a collection of lower level \index{heuristic}heuristics, called a \index{heuristic pool}\textit{heuristic pool}. Selection is biased towards good performing heuristics. A credit assignment strategy is used to \textit{reward} good heuristic performance. The \acs{BHH} maintains entity and population state through operations that \textit{proxy} update steps from different heuristics (perturbation), as is required. These proxy operations ensure that heuristic requirements are satisfied even when different heuristics are used for different entities throughout the training process.

      \item \textbf{Online Learning:} The \acs{BHH} applies learning, at specified intervals, throughout the \acs{FFNN} training process.
\end{itemize}

\noindent
The following sections presents the reader with more detail on the implementation of the \acs{BHH}. Discussions lead with the \acs{BHH} architecture and general \acs{HH} framework in the following section.

\section{Architecture}\label{sec:bhh:architecture}

This section aims to present the reader with all the high level components in the architecture of the \Acs{BHH}. Burke et al.~\cite{ref:burke:2010} proposed an initial framework for \acp{HH} and Grobler~\cite{ref:grobler:2015} further proposed a framework for a heterogeneous meta-\ac{HH}. The aforementioned frameworks are adapted for the implementation of the \Acs{BHH}. An illustration of the high-level architecture of the \Acs{BHH} is given in Figure \ref{fig:bhh_architecture}.

\begin{figure}[htbp]
      \centering
      \includegraphics[width=1.0\textwidth]{bhh_architecture.pdf}
      \caption[An illustration of
            the architecture and high level components of the \acf{BHH}.]{An illustration of
            the architecture and high level components of the \acf{BHH}.}
      \label{fig:bhh_architecture}
\end{figure}

\noindent
With reference to Figure \ref{fig:bhh_architecture}, the components are briefly given below in the order of information flow during the \acs{FFNN} training process steps.

\begin{itemize}
      \item \textbf{Initialisation Step}: The initialisation step refers to the initialisation strategy implemented by the \acs{BHH}.

      \item \textbf{Heuristic Pool}: The \index{heuristic pool}heuristic pool contains a collection of low-level \index{heuristic}heuristics.

      \item \textbf{Entity Pool}: The \index{entity pool}entity pool represents a collection of candidate solutions for the underlying \acs{FFNN}, referred to as entities in a population.

      \item \textbf{Selection Mechanism}: The selection mechanism refers to the Bayesian probabilistic model.

      \item \textbf{Heuristic-Entity Selections}: Every entity in the \index{entity pool}entity pool gets assigned a selected heuristic.

@@

      \item \textbf{Model}: The underlying \acs{FFNN} to be trained.

      \item \textbf{Low-Level Heuristics Update Step}: The low-level heuristics' update step as it applies to its allocated entity.

      \item \textbf{Loss Function}: In supervised learning, the loss function is a measure of distance between predicted output and the ground truth, and is the mechanism used to evaluate the model's performance.

      \item \textbf{Domain Barrier}: The domain barrier is the logical separation of information available in the heuristic space and the solution space. The \acs{BHH} searches in the heuristic space, while low-level heuristics search in the solution space.

@@

      \item \textbf{Credit Assignment Strategy}: The strategy used to assign credit to heuristics for their performance.

      \item \textbf{Update Step}: The high-level heuristic update step as implemented by the \acs{BHH}.
\end{itemize}

\noindent
Each of the components in Figure \ref{fig:bhh_architecture} is discussed in detail in the following sections.

\index{heuristic pool}
\section{Heuristic Pool}\label{sec:bhh:heuristic_pool}

Generally speaking, the \index{heuristic pool}heuristic pool is a collection of low-level heuristics under consideration by the \acs{BHH}. The \index{heuristic pool}heuristic pool contains the set of low-level \index{heuristic}heuristics that, together with their performance information, make up the \text{heuristic space}. Importantly, the \acs{BHH} searches in \index{heuristic}heuristic space. The \index{heuristic pool}heuristic pool is defined in terms of the diversity of heuristics, as well as the amount of heuristics in the \index{heuristic pool}heuristic pool. Each of these are discussed in the following sections.

\subsection{Heuristic Diversity}\label{sec:bhh:heuristic_pool:diversity}

A \index{heuristic}heuristic's eligibility for inclusion in the \index{heuristic}heuristic pool, is determined by its ability to solve to underlying problem and its search behaviour and characteristics. The \index{heuristic pool}heuristic pool should contain a variety of different heuristics that have different search behaviours, so that a trade-off can be made by between exploration and exploitation of solutions, as is required during the training process. Heuristics that explore a lot, should be selected when exploration is needed, and heuristics that exploit a lot should be selected accordingly. The trade-off between exploration and exploitation is managed by the high-level heuristic. The \acs{BHH} will learn to select and apply the appropriate heuristic, at the appropriate points, throughout the training process. In doing so, a balance is achieved between exploration and exploitation.

\subsection{Heuristic Pool Size}\label{sec:bhh:heuristic_pool:pool_size}

Another design decision in the heuristic pool is heuristic pool size. Since the \acs{BHH} is a \textit{learning} \acs{HH}, every heuristic that is included in the heuristic pool increases the requirement of more statistical evidence of heuristic performance. Not only does a large \index{heuristic pool}heuristic pool drastically complicate the learning process that is required by the \ac{BHH}, but it also drastically complicates the process of maintaining \textit{state}. State is the term used to describe data that is relevant to the training process, and is maintained between training steps. An example of \textit{local} state is an entity's position, while an example of \textit{global} state is the global best solution found thus far. The following section presents the concept of \textit{proxies} and their role in maintaining state.

\subsection{Proxies}\label{sec:bhh:heuristic:proxies}

The concept of proxies arise from the sparsity of state as maintained by different \index{heuristic}heuristics. Since \index{heuristic}heuristics maintain (possibly) different states, there is an uncertainty of state transition when switching between \index{heuristic}heuristics. Consider an example where the \index{heuristic pool}heuristic pool consists of just two \index{heuristic}heuristics. One heuristic is a gradient-based heuristic that maintains momentum such as \acs{Adam}. The other is a \index{meta-heuristic}meta-heuristic that does not require a gradient, such as \acs{PSO}. Both these \index{heuristic}heuristics track different parameters in their state. For \acs{Adam}, the expected gradient mean and variance is maintained, while the \ac{PSO} maintains record of the gbest and pbest solutions of all of entities. A solution to state indifference, is to proxy heuristic state update operations. State is then maintained in two parts:

\begin{itemize}
      \item \textbf{Primary State}: Refers to the state that is originally maintained by a heuristic. The selected heuristic simply applies the normal state update operations to its state.

      \item \textbf{Proxied State}: Refers to the state that is not directly maintained by the heuristic, but can be updated by outsourcing the required state update operation to another heuristic.
\end{itemize}

\noindent
Primary and proxied state parameters must be maintained together. Since entities represent candidate solutions, which are forms of state, entities are ideal candidates to store and maintain these state parameters. Entities are extended to include the primary state elements of \textit{all} the underlying low-level heuristics, as well as the candidate solution (weights) for the \acs{FFNN}. At each heuristic-entity application step, all state elements per entity are updated either by primary method or by proxied method. The \ac{BHH} thus incorporates a mapping of proxied state update operation as given in the example in Table \ref{tab:bhh:heuristic_pool:proxy_mapping_example} below.

\begin{table}[htbp]
      \centering
      \caption{An example of mapping of proxied state update operation maintained by the \acs{BHH}.}
      \label{tab:bhh:heuristic_pool:proxy_mapping_example}%
      \par\bigskip
      \resizebox{0.5\textwidth}{!}{
            \begin{tabular}{ccccc}
                                                                  &   & \multicolumn{3}{c}{State Parameter}                                                                                                                                                                                      \\
                  \cmidrule{3-5}                                  &   & 1                                                                      & 2                                                                      & 3                                                                      \\
                  \cmidrule{3-5}    \multirow{3}[1]{*}{Heuristic} & A & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{n/a} & \cellcolor[rgb]{ 1,  .922,  .612}\textcolor[rgb]{ .612,  .341,  0}{B}  & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{n/a} \\
                                                                  & B & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{n/a} & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{n/a} & \cellcolor[rgb]{ 1,  .922,  .612}\textcolor[rgb]{ .612,  .341,  0}{A}  \\
                                                                  & C & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{n/a} & \cellcolor[rgb]{ 1,  .922,  .612}\textcolor[rgb]{ .612,  .341,  0}{B}  & \cellcolor[rgb]{ 1,  .922,  .612}\textcolor[rgb]{ .612,  .341,  0}{A}  \\
            \end{tabular}%
      }
\end{table}%

\noindent
From the example given in Table \ref{tab:bhh:heuristic_pool:proxy_mapping_example}, when \index{heuristic}heuristic A is selected, it will outsource state update operations from \index{heuristic}heuristic B, for state parameter 2. Heuristic B will outsource from \index{heuristic}heuristic A, for state parameter 3. Finally, \index{heuristic}heuristic C will outsource from \index{heuristic}heuristic A and B, for state parameters 2 and 3 respectively. In this way, all \index{heuristic}heuristics maintain all the state parameters.

Proxied state update operations is a simple concept in principle, but requires detailed decomposition of the \index{heuristic}heuristics included in the \index{heuristic pool}heuristic pool.  Overlapping and unique state parameters must be identified so that a proxy mapping, such as the one given in Table \ref{tab:bhh:heuristic_pool:proxy_mapping_example}, can be constructed. A suggestion to simplify this process is to borrow concepts from the equations of motion from physics. These include \textit{position}, \textit{velocity}, \textit{acceleration} and \textit{momentum}. Expressing \index{heuristic}heuristic update steps according to these parameters drastically simplify the process. However, it is possible that \index{heuristic}heuristics implement unique state parameters that do not overlap, these have to be catered for in the proxy mapping.

State parameters and update operations should not be considered in isolation. An example is \textit{position} and \textit{velocity}. Consider, for example, \index{heuristic}heuristics such as \acf{DE} and \acfp{GA}. These \index{heuristic}heuristics recombine entities. In the aforementioned case, the concept of an equation of motion does not entirely make sense, since the displacement of its position is not a result of maintaining velocity or momentum, but rather by displacement through recombination. In this particular case, a solution is to apply the recombination operation to \textit{all} applicable state parameters as well, or to nullify the necessary state parameters. Unfortunately there is no general, automated solution to formulate these heuristic state overlaps. Each \index{heuristic}heuristic must be carefully considered. More details on the \index{entity pool}entity pool and entity state are presented in the following section.

\index{entity pool}
\section{Entity Pool}\label{sec:bhh:entity_pool}

The \index{entity pool}entity pool refers to a collection of \textit{entities} that each represent a candidate solution to the underlying \acs{FFNN} being trained. The entities contain information of the solution space. A common naming convention for such a collection is a \textit{population} of entities. The \acs{BHH} is a population-based \acs{HH} and as such, the \index{entity pool}entity pool size or population size is an important design choice. The population size is defined as a hyper-parameter of the \acs{BHH} and can be empirically evaluated.

The \index{entity pool}entity pool maintains two different types of state. These include entity (local) and population (global) state. Each of these are discussed in more detail next.

\subsection{Entity State}\label{sec:bhh:entity_pool:entity_state}
